### 2023-04-18 paper.Rmd
minor

As discussed in the previous section, an exclusive maximization of $\mathit{SSE_{Var}}$ (i.e., equalizing variances) is not feasible without also considering the standard $\mathit{SSE}$ (i.e., equalizing means). Moreover, an exclusive maximizing of $\mathit{SSE_{Var}}$ is most likely not even interesting in any real application. Hence, when striving for similarity in group variances by maximizing $\mathit{SSE_{Var}}$, it is at the same time necessary and worthwhile to strive for similarity in means, and thus to maximize $\mathit{SSE}$ at the same time. The most simple approach for a multicriterion optimization is the weighted sum approach [@naidu2014; @marler2010]. That is, all criteria are computed independently from each other and are then combined into a single criterion through a weighted sum. By combining $\mathit{SSE_{Var}}$ and $\mathit{SSE}$ in a single criterion, we define the objective function for k-plus anticlustering:

>>>>

As discussed in the previous section, an exclusive maximization of $\mathit{SSE_{Var}}$ (i.e., equalizing variances) is not feasible without also considering the standard $\mathit{SSE}$ (i.e., equalizing means). Moreover, maximizing only $\mathit{SSE_{Var}}$ is most likely not interesting in any real application. Hence, when striving for similarity in group variances by maximizing $\mathit{SSE_{Var}}$, it is at the same time necessary and worthwhile to strive for similarity in means, and thus to maximize $\mathit{SSE}$ at the same time. The most simple approach for a multicriterion optimization is the weighted sum approach [@naidu2014; @marler2010]. That is, all criteria are computed independently from each other and are then combined into a single criterion through a weighted sum; a suitable optimization algorithm is then used to maximize the combined criterion. By combining $\mathit{SSE_{Var}}$ and $\mathit{SSE}$ in a single criterion, we define the objective function for k-plus anticlustering:
